Likelihood-Based Inference for Generalized Linear Mixed Models: Inference with Package \pkg{glmm}

### 2017-02-14 JSS/article.tex
editing sect 3
moving salamander description, adding r analysis

\subsection{Examples}\label{sec:examples}
We  illustrate \pkg{glmm} with two data sets: the salamander data set serves as an example for modeling binomial-distributed data while the radish flower data set serves as an example for modeling Poisson-distributed data.

\subsubsection{The salamander data}\label{sec:salex}

\subsubsection{The radish flower data}

@@

@@

\subsection{Salamander data analysis}

Recall the salamander experiment described in Section \ref{sec:examples}. For your convenience, the \texttt{salamander} dataset is  included in the \texttt{glmm} package. The data arose from an experiment conducted at the University of Chicago in 1986 and were first presented by \citet[section 14.5]{mcc:nelder:1989}.  \\

The variable \texttt{Mate} tells us whether the pair of salamanders mated. The value is $1$ if they successfully mated and $0$ if they did not. The variable \texttt{Cross} describes the type of female and male salamander. For example, \texttt{Cross = W/R} indicates a White Side female was crossed with a Rough Butt male. The variable \texttt{Female} contains the identification number of the female salamander, and the variable \texttt{Male} contains the identification number of the male salamander.\\

The first \proglang{R}  command shown below gives us access to the \texttt{glmm} package and and all of its commands. The second line of code gives us access to the \texttt{salamander} data frame.  The next three commands help us begin to understand the data. We have four variables: \texttt{Mate}, \texttt{Cross}, \texttt{Female}, and \texttt{Male}. The summary shows us \texttt{Mate} is numeric, \texttt{Cross} is a factor with four levels, \texttt{Female} is a factor, and \texttt{Male} is a factor.

\begin{CodeChunk}
\begin{CodeInput}
first input first line
first input second line
\end{CodeInput}
\begin{CodeOutput}
output of first input
\end{CodeOutput}
\begin{CodeInput}
second input
\end{CodeInput}
\end{CodeChunk}

>>>>

@@

\section{Examples}\label{sec:examples}
We  illustrate \pkg{glmm} with two data sets: the salamander data set serves as an example for modeling binomial-distributed data while the radish flower data set serves as an example for modeling Poisson-distributed data. This section provides background information on  the research conducted and Section \ref{sec:howto} demonstrates the analysis using \pkg{glmm}.

\subsection{The salamander data}\label{sec:salex}

 For your convenience, the \texttt{salamander} dataset is  included in the \texttt{glmm} package. The first \proglang{R}  command shown below gives us access to the \texttt{glmm} package and and all of its commands. The second line of code gives us access to the \texttt{salamander} data frame.  The next three commands help us begin to understand the data. We have four variables: \texttt{Mate}, \texttt{Cross}, \texttt{Female}, and \texttt{Male}. The summary shows us \texttt{Mate} is numeric, \texttt{Cross} is a factor with four levels, \texttt{Female} is a factor, and \texttt{Male} is a factor.

\begin{CodeChunk}
\begin{CodeInput}
library(glmm)
data(salamander)
names(salamander)
\end{CodeInput}
\begin{CodeOutput}
[1] "Mate" "Cross" "Female" "Male"
\end{CodeOutput}
\begin{CodeInput}
head(salamander)
\end{CodeInput}
\begin{CodeOutput}
   Mate Cross Female Male
 1    1   R/R     10   10
 2    1   R/R     11   14
 3    1   R/R     12   11
 4    1   R/R     13   13
 5    1   R/R     14   12
 6    1   R/W     15   28
\end{CodeOutput}
\end{CodeChunk}

The variable \texttt{Mate} tells us whether the pair of salamanders mated: the value is $1$ if they successfully mated and $0$ if they did not. The variable \texttt{Cross} describes the type of female and male salamander. For example, \texttt{Cross = W/R} indicates a White Side female was crossed with a Rough Butt male. The variable \texttt{Female} contains the identification number of the female salamander, and the variable \texttt{Male} contains the identification number of the male salamander.\\

\subsection{The radish flower data}

@@

\begin{CodeChunk}
\begin{CodeInput}
input code
\end{CodeInput}
\begin{CodeOutput}
output code
\end{CodeOutput}
\begin{CodeInput}
second input
\end{CodeInput}
\end{CodeChunk}
